---
title: "Homework 2"
author: "Eric Gleiter: Github- Eric-Gleiter"
date: "2/3/2020"
output: html_document
---

Question 1) 
```{r}
    cel = c(-4.44444,-9.44444)
    cel
```

Question 2)
```{r}
vector = c(1,3)
for (i in 3:200)
{
  if (i%%2 == 1)
  {
    vector = c(vector,1)
  }
  else
  {
    vector = c(vector,3)
  }
}
vector
```

Question 3)
```{r}
numPerfect = floor(sqrt(2001))
numPerfect
```
there are 44 perfect squares between 1 and 2001

**Cars and Mileage**
```{r}
if (!require("ggplot2")) {
install.packages("ggplot2")
}
library(ggplot2)
```

Question 1)
```{r}
mpgcopy <- mpg
hwympg <- mpgcopy$hwy
mpgcopy <- mpgcopy[order(hwympg),]
top3 <- tail(mpgcopy,3)
top3
```
The top3 three are the jetta and new beetle (auto and manual) I found this by sorting the data frame by the highway mileage and then pulling out the 3 best mileages.

Question 2)
```{r}
compacts <- mpgcopy$class
numCompact <- 0
for (i in 1:length(compacts))
{
  if (compacts[i] == 'compact')
  {
    numCompact <- numCompact +1
  }
}
numCompact
```
There are 47 compact models in this data set


Question 3)
```{r}
ctympg <- mpgcopy$cty
plot(ctympg, hwympg)

```

When I plotted the two, I was able to see a large amounts of points however I assumed the reason some people would not see a lot of points would be if points overlapped as in multiple points in one location. Additionally when looking at this plot I believe there is a very slight trend upwards suggesting that cty and hwy mpg are positively correlated.

Question 4)
```{r}
mpgcopy$fuel <- (mpgcopy$cty + mpgcopy$hwy)/2
year <- mpgcopy$year
plot(year, mpgcopy$fuel)

if (!require("psych")) {
install.packages("psych")
}
library(psych)
describeBy(mpgcopy$fuel, mpgcopy$year)
```

First In order to compare fuel I used the average of the highway (hwy) and the city (city) fuel efficiencies. Looking at the graph we see what appears to be more cars having a higher fuel efficiency in 1999 suggested by the outliers. However looking at the summary statistics we can see the difference in means is very small with a very similar spread this suggest that there is not significant difference in the fuel efficiency of the two types of cars a t-test would most likely confirm this hypothesis.